\papertitle

### 2021-03-11 source_separation/paper/paper.tex
Carmine's changes

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the computer-assisted orchestration process. We first discuss the motivation of this addition and its potential to increase the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assess which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improves, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we compare unsupervised methods to supervised methods for separation, and the effect of training data selection on performance for supervised methods.
	\end{abstract}
	%

@@

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized optimization heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

@@

		Suggestion: A block-diagram of the algo would be nice to have

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed. Lower values are better.}
		\label{tab:distances}
	\end{table}

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations on average. TDCN++, Open-Unmix, and NMF performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

	\section{Discussion}\label{sec:conclusions}
	In this paper, we addressed the problem of using source separation as a pre-processing step for computer-assisted orchestration. The results show that performing source separation followed by a static orchestration of each individual sub-target improved the spectral distance between the original target and its orchestrated version in three out of five of the methods tested. This shows that source separation is a useful pre-processing stage for computer assisted orchestration.

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.

	TODO: say that unsupervised methods can still do well in particular cases where there are not many examples

@@

		As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.

>>>>

	\begin{abstract}
		In this paper, we will study the possibility of adding source separation as a pre-processing step to the computer-assisted orchestration process. We first discuss the motivation of this addition and its potential to increase the quality of orchestrations of multi-layered sounds. Second, we select several state-of-the-art models for both music source separation (separation of instruments) and universal sound separation (separation of arbitrary sounds of different types), and compare their effectiveness for the task of orchestration. We assess which methods best suit the needs of orchestration by applying them on hand picked target sounds, orchestrating the separated outputs, and finally comparing them to the orchestration of the same target without separation. Our experiments show that the quality of orchestrations improves, both qualitatively and quantitatively, indicating that our approach is promising. Finally, we compare unsupervised methods to supervised methods for separation, and comment on the effect of training data selection on performance of supervised methods.
	\end{abstract}
	%

@@

	 Orchidea is a framework and set of tools that is currently considered the state-of-the-art for computer-assisted orchestration. Orchidea embeds the target in a feature space and uses a jointly-optimized heuristic and constraint solver to find a combination of samples that best match the target~\cite{Cella18, Cella2020}.

@@

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
		\label{tab:distances}
	\end{table}

		\subsection{Results}
		The average distances for full target, separated, and ground truth orchestrations are displayed in Table \ref{tab:distances}. These results are the average distance between target and orchestration for 300 different targets. We found that NMF performed the best out of all separation methods, and even outperformed the ground truth orchestrations, on average. TDCN++, Open-Unmix, and NMF performed better than the full target orchestrations, meaning that separating targets using these methods leads to a better orchestration than if no separation is applied.

	\section{Discussion}\label{sec:discussion}
	In this paper, we addressed the problem of using source separation as a pre-processing step for computer-assisted orchestration. The results show that performing source separation followed by a static orchestration of each individual sub-target improved the spectral distance between the original target and its orchestrated version in three out of five of the methods tested. This shows that source separation is a useful pre-processing stage for computer-assisted orchestration.

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. When training data for a particular problem is scarce, it is logical that unsupervised methods will perform well, as they do not rely on training data. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.

@@

		As we stated previously, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models with sounds that are more appropriate for computer-assisted orchestration.
